Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-01-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Deleted excess biblio material from header

@manual{ID,
	ALTauthor = {author},
	ALTeditor = {editor},
	title = {title},
	date = {date},
	OPTsubtitle = {subtitle},
	OPTtitleaddon = {titleaddon},
	OPTlanguage = {language},
	OPTedition = {edition},@unpublished{ID,
		author = {author},
		title = {title},
		date = {date},
		OPTsubtitle = {subtitle},
		OPTtitleaddon = {titleaddon},
		OPTlanguage = {language},
		OPThowpublished = {howpublished},
		OPTnote = {note},
		OPTlocation = {location},
		OPTisbn = {isbn},
		OPTdate = {date},
		OPTmonth = {month},
		OPTyear = {year},
		OPTaddendum = {addendum},
		OPTpubstate = {pubstate},
		OPTurl = {url},
		OPTurldate = {urldate},
	}

	OPTtype = {type},
	OPTseries = {series},
	OPTnumber = {number},
	OPTversion = {version},
	OPTnote = {note},
	OPTorganization = {organization},
	OPTpublisher = {publisher},
	OPTlocation = {location},
	OPTisbn = {isbn},
	OPTchapter = {chapter},
	OPTpages = {pages},
	OPTpagetotal = {pagetotal},
	OPTaddendum = {addendum},
	OPTpubstate = {pubstate},
	OPTdoi = {doi},
	OPTeprint = {eprint},
	OPTeprintclass = {eprintclass},
	OPTeprinttype = {eprinttype},
	OPTurl = {url},
	OPTurldate = {urldate},
}
\documentclass[twoside]{uocthesis}

>>>>

\documentclass[twoside]{uocthesis}
